Deep Reinforcement Learning for Conservation Decisions

### 2020-12-08 manuscript/manuscript.Rmd
a bit more context

```{r}
# Simulate under the optimal solution (given the model)
opt <- gym_fishing$models$escapement(env)
opt_sims <- env$simulate(opt, reps = 500L)
opt_policy <- env$policyfn(opt) %>% rename(optimal = action)

sims_df <- bind_rows(sims, opt_sims, .id = "model")
policy <- left_join(policy, opt_policy)
```

@@

```{r fig1, fig.cap=""}
fig_sims + fig_policy
```

>>>>

```{r}
# Simulate under the optimal solution (given the model)
opt <- gym_fishing$models$escapement(env)
opt_sims <- env$simulate(opt, reps = 500L)
opt_policy <- env$policyfn(opt) %>% rename(optimal = action)
```

```{r}
sims_df <- bind_rows(sims, opt_sims, .id = "model") %>%
  mutate(model = c("A2C", "optimal")[as.integer(model)])

policy <- left_join(policy, opt_policy)
```

```{r}
gamma <- 1 #discount
fig_reward <- sims_df %>% 
  group_by(rep, model) %>%
  mutate(cum_reward = cumsum(reward * gamma^time)) %>%
  group_by(time, model) %>%
  summarise(mean_reward = mean(cum_reward), 
            sd = sd(cum_reward), .groups = "drop") %>% 
  ggplot(aes(time, mean_reward)) + 
  geom_ribbon(aes(ymin = mean_reward - 2*sd, 
                  ymax = mean_reward + 2*sd, fill = model),
              alpha=0.25, show.legend = FALSE) + 
  geom_line(aes(col = model)) + ylab("mean cumulative reward")
```

@@

```{r fig1, fig.cap=""}
fig_sims / ( fig_policy + fig_reward)
```
Note that the A2C policy learns to shut down fishing entirely below a certain stock size, without any variation.  However, it keeps the fishery closed even once stock sizes are slightly higher than $B_{MSY}$.  Once it begins fishing, it slightly under-harvests for stock sizes a little over $B_{MSY}$, but tends to over-harvest for very large stock sizes (rarely ever realized, as fishing pressure is enough to keep it out of this range). Note also that the harvest varies across replicates, creating a fuzzy region in the policy function. Under such a policy, A2C maintains a stock size on average significantly above $B_{MSY}$, though also sees higher volatility particularly on the low side.  Note that due to the stochastic nature of the environment, any given replicate A2C may out-perform the optimal policy, though on average the optimal policy provides consistently better yields.
